Make a table for hypothesis

### 2021-04-26 manuscript/bef_stability/review_analysis.Rmd
Updates

theme_set(theme_alain())

@@

```{r}
synchrony %>%
  ggplot(aes(y = cv_sp * sqrt(synchrony), x = cv_classic)) +
  geom_point() +
  labs(y = "CVsp * sqrt(synchrony)", x = "CV of biomass")
```

@@

mod <- lm(log_stab_std ~ 0 + log_cv_sp + log_sync, data = sem_data)

#summary(mod)
coefs <- broom::tidy(mod) %>%
  select(term,estimate)

@@

@@

p_sens_stab <- plot_sensivity_analysis(
  .data = sem_stab_results_2006,
  inverse_label_order = TRUE, 
  y_lim = c(-1.5, .75)
  ) +
scale_color_manual(
  values = c("full" = "red", "from_2006" = "blue"),
  labels = c("Full dataset", "Dataset from 2006"),
  breaks = c("full", "from_2006") 
  ) +
  guides(color = guide_legend(direction = "horizontal", nrow = 1)) +
  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
```

@@

p_sens_bm <- plot_sensivity_analysis(
  .data = sem_bm_results_2006,
  inverse_label_order = TRUE,
  y_lim = c(-1.5, .75)
  ) +
scale_color_manual(
  values = c("full" = "red", "from_2006" = "blue")
  ) +
  guides(color = guide_legend(direction = "horizontal", nrow = 1)) +
  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
```

```{r start-sens, fig.dim = c(14, 10), fig.cap="Sensivity of standardized estimate to the station starting date."}
legend_b <- get_legend(p_sens_stab)

p <- plot_grid(
  p_sens_bm %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm")),
  p_sens_stab %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm")),
  legend_b, nrow = 3,
  rel_heights = c(1, 1, .1),
  labels = c("Total biomass", "Biomass stability")
)
p
```

@@

@@

p_sens_bm_rich <- plot_sensivity_analysis(
  .data = sem_bm_results_rich,
  inverse_label_order = TRUE, scale_color = FALSE,
  y_lim = c(-1.5, .75)
  ) +
scale_color_manual(
  values =  cols_rich,
  labels = label_rich,
  breaks = names(label_rich)) +
  guides(color = guide_legend(direction = "horizontal", nrow = 1)) +
  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
```

@@

```{r rich-sens, fig.dim = c(14, 10), fig.cap="Sensivity of the standardized estimates to species richeness specification for the two structural equation model."}
legend_b <- get_legend(p_sens_stab_rich)
p <- plot_grid(
  p_sens_bm_rich %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm")),
  p_sens_stab_rich %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm")),
  legend_b, nrow = 3,
  rel_heights = c(1, 1, .1),
  labels = c("Total biomass", "Biomass stability")
)
p
```

The choice of richness variable would

# Response to comment R3-Section 5.3

>>>>

theme_set(theme_cowplot())

@@

```{r}
p_sync <- synchrony %>%
  ggplot(aes(y = cv_sp * sqrt(synchrony), x = cv_classic)) +
  geom_point() +
  labs(y = "CVsp * sqrt(synchrony)", x = "CV of biomass")
```

@@

```{r, echo = TRUE}
mod <- lm(log_stab_std ~ 0 + log_cv_sp + log_sync, data = sem_data)

#summary(mod)
coefs <- broom::tidy(mod) %>%
  select(term, estimate)

@@

# Response to the comment

```{r}
source(mypath("R", "synchrony.R"))

myload(community_analysis, op_analysis, synchrony, dir = mypath("data"))

myload(network_metrics, network_analysis, dir = mypath("data", "classes"))
```

```{r}
compute_pair_synchrony <- function (com_mat = NULL) {
  sp_names <- colnames(com_mat)
  ti <- combn(sp_names, 2,
    FUN = function (x) {
      covar <- cov(x = com_mat[, x[1:2]])
      #  vars <- var(c(mat[, x[1]], mat[, x[2]])) 
      sync <- compute_synchrony(covar)
      names(sync) <- paste(x[1], x[2], sep = "-")
      return(sync)
    }, simplify = FALSE
  )
  unlist(ti)
}
```

net <- left_join(network_metrics, op_analysis, by = "opcod") %>%
  ungroup() %>%
  filter(!is.na(station))

prep_troph_sp_biomass <- net %>%
  select(opcod, station, year, composition, surface) %>%
  unnest(composition) %>%
  mutate(bm_std = biomass/ surface)

troph_sp_biomass <- prep_troph_sp_biomass %>%
  select(station, year, sp_class, bm_std) %>%
  group_by(station) %>%
  nest() %>%
  mutate(
    com_mat = map(data, function(x) {
      ti <- x %>%
	pivot_wider(names_from = sp_class, values_from = bm_std) %>%
	mutate_at(vars(matches("[A-Z]{3}", ignore.case = FALSE)),
	  ~ifelse(is.na(.), 0, .))
    return(as.matrix(select(ti, -year)))
}
    )
  )

library(furrr)
library(parallel)
plan(multisession, workers = 3)

sync_troph_sp <- troph_sp_biomass %>%
  ungroup() %>% # For furrr to works
  mutate(sync = future_map(com_mat, ~compute_pair_synchrony(.x)))

```{r}
get_if_fish_pair_interact <- function (net = NULL) {

  te <- net[
    str_detect(colnames(net), "[A-Z]{3}"),
    str_detect(colnames(net), "[A-Z]{3}")
    ]

  sp_names <- colnames(te)
  ti <- combn(sp_names, 2,
    FUN = function (x) {
      int <- as.logical(te[x[2], x[1]])
      names(int) <- paste(x[1], x[2], sep = "-")
      return(int)
    }, simplify = FALSE
  )
  unlist(ti)
}
```

```{r}
myload(metaweb_analysis, dir = mypath("data"))
metaweb <- metaweb_analysis$metaweb

pair_int <- get_if_fish_pair_interact(metaweb)
metaweb["ANG_2", "TRF_8"]

```{r}
get_sync_int <- function(sync = NULL, pair_int = NULL) {

  # compute inv prey-pred names to have symetric name combination   
  pair_site <- names(sync)
  inv_pair_site <- str_split(pair_site, "-") %>% map_chr(., ~paste0(.x[2], "-",.x[1]))

  tmp <- pair_int[c(pair_site, inv_pair_site)]
  pair_int_com <- tmp[!is.na(tmp)]

  replace_pair_inv_pair <-  pair_site
  names(replace_pair_inv_pair) <- inv_pair_site 
  names(pair_int_com) <- str_replace_all(names(pair_int_com), replace_pair_inv_pair)

  df_pair <- enframe(pair_int_com, name = "pair", value = "interact")
  df_sync <- enframe(sync, name = "pair", value = "sync")

  df_sync %<>%
    left_join(df_pair, by = "pair")

  return(df_sync)
}
```

pair_site <- names(sync_troph_sp$sync[[1]])
inv_pair_site <-str_split(pair_site, "-") %>% map_chr(., ~paste0(.x[2], "-",.x[1]))
tmp <- pair_int[c(pair_site, inv_pair_site)]
pair_int_com <- tmp[!is.na(tmp)]

get_sync_int(sync_troph_sp$sync[[1]], pair_int = pair_int)

```{r, eval=FALSE}
sync_troph_sp %<>%
  mutate(sync_int = future_map(sync, get_sync_int, pair_int = pair_int))

sync_pair_int <- sync_troph_sp %>%
  select(station, sync_int) %>%
  unnest(sync_int)

mysave(sync_pair_int, dir = mypath("data"), overwrite = TRUE)
```

```{r}
myload(sync_pair_int, dir = mypath("data"))
sync_pair_int2 <- sync_pair_int %>%
  separate(pair, c("sp1", "sp2"), "-") %>%
  mutate_at(c("sp1", "sp2"), ~str_extract(., "[A-Z]{3}")) %>%
  mutate(cannibalism = map2_lgl(sp1, sp2, ~ifelse(.x == .y, TRUE, FALSE)))
```

There is no cannibalism case!

```{r}
sync_pred <- sync_pair_int2 %>%
  ggplot(aes(y = sync, x = as.factor(interact)), fill = as.factor(cannibalism)) +
  geom_boxplot() +
  facet_grid(~cannibalism) +
  labs(y = "Synchrony", x = "Species in interaction", fill = "Cannibalism")
```

```{r}
sync_pred <- sync_pair_int2 %>%
  ggplot(aes(y = sync, x = as.factor(interact))) +
  geom_boxplot() +
  labs(y = "Synchrony", x = "Species pairs in interaction", fill = "Cannibalism")
```

```{r}
save_plot(file = mypath(
      "manuscript", "bef_stability", "result", 
      "synchrony_species_pairs.png"),
    plot = sync_pred,
    base_height = 2.5, base_asp = 1.2#1.618 
    )
```

@@

p_sens_stab <- plot_sensivity_analysis(
  .data = sem_stab_results_2006,
  inverse_label_order = TRUE, 
  y_lim = c(-1.5, .75), pval = TRUE
  ) +
scale_color_manual(
  values = c("full" = "red", "from_2006" = "blue"),
  labels = c("Full dataset", "Dataset from 2006"),
  breaks = c("full", "from_2006") 
  ) +
  guides(color = guide_legend(direction = "horizontal", nrow = 1)) +
  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))+
  labs(shape = "P <= 0.05")
```

```{r}
save_plot(file = mypath(
      "manuscript", "bef_stability", "result", 
      "sensivity_stab_2006.png"),
    plot = p_sens_stab,
    base_height = 9, base_asp = 1.2#1.618 
    )
```

@@

p_sens_bm <- plot_sensivity_analysis(
  .data = sem_bm_results_2006,
  inverse_label_order = TRUE,
  y_lim = c(-1.5, .75), pval = TRUE
  ) +
scale_color_manual(
  values = c("full" = "red", "from_2006" = "blue")
  ) +
  guides(color = guide_legend(direction = "horizontal", nrow = 1)) +
  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))+
  labs(shape = "P <= 0.05")
```

```{r}
save_plot(file = mypath(
      "manuscript", "bef_stability", "result", 
      "sensivity_bm_2006.png"),
    plot = p_sens_bm,
    base_height = 9, base_asp = 1.2#1.618 
    )
```

```{r start-sens, fig.dim = c(10, 14), fig.cap="Sensivity of standardized estimate to the station starting date."}
legend_b <- get_legend(p_sens_stab)

p <- plot_grid(
  p_sens_bm %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm")),
  p_sens_stab %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm")),
  legend_b, nrow = 3,
  rel_heights = c(1, 1, .1),
  labels = c("Total biomass", "Biomass stability")
)
p
save_plot(
  file = mypath( "manuscript", "bef_stability", "result", 
      "sensivity_2006.png"),
    plot = p,
    nrow = 2,
    base_height = 9, base_asp = 1.6#1.618 
)
```

# Second answer

- get air temperature data 
- match them with water temperature (raw or interpolated?)

```{r}
#devtools::install_github("RetoSchmucki/climateExtract")
library(climateExtract)
library(ncdf4)

fr_border <- sf::st_as_sf(raster::getData("GADM", country = "FRA", level = 0))
debug(extract_nc_value)
climate_data = extract_nc_value(first_year = 1995, 
                                last_year = 2018,
                                local_file = FALSE,
                                file_path = NULL,
                                sml_chunk = "2011-2020",
                                spatial_extent = fr_border,
                                clim_variable = "mean temp",
                                statistic = "mean",
                                grid_size = 0.25,
                                ecad_v = NULL,
                                write_raster = TRUE,
                                out = "raster_mean_temp.grd",
                                return_data = TRUE)
# Get annual mean for each point 
annual_avg_temp_pnts = temporal_aggregate(x = rbk,
                                          y = sf_point,
                                          agg_function = "mean",
                                          variable_name = "average temp",
                                          time_step = "annual")
```

```{r}
library(reprex)
library(climateExtract)
climate_data = extract_nc_value(first_year = 2012, 
                                last_year = 2015,
                                local_file = FALSE,
                                file_path = NULL,
                                sml_chunk = "2011-2020",
                                spatial_extent = fr_border,
                                clim_variable = "mean temp",
                                statistic = "mean",
                                grid_size = 0.25,
                                ecad_v = NULL,
                                write_raster = TRUE,
                                out = "raster_mean_temp.grd",
                                return_data = TRUE)
```

```{r}
library(climate)

po <- nearest_stations_ogimet(country = "France",
  date = Sys.Date(),
  add_map = TRUE,
  no_of_stations = 500 
)

o = meteo_ogimet(date = c("1995-01-01", "2018-12-31"), 
                 interval = "daily",
                 coords = FALSE, 
                 station = "07005")
```

```{r}
library(ncdf4)
library(raster)
library(sf)
cru_file <- list.files(mypath("data-raw", "cru"))[!str_detect(list.files(mypath("data-raw", "cru")), "gz")]
nc.pre <- nc_open(mypath("data-raw", "cru", "cru_ts4.03.2011.2018.tmp.dat.nc"))

l <- map(cru_file, function (x) {
  pre <- raster::brick(mypath("data-raw", "cru", x), varname="tmp")
  extract(pre, st_wgs)
		 }
)

tmean <- do.call(cbind, l)
rownames(tmean) <- st_wgs$station
colnames(tmean) <- paste0(rep(c(paste0(0, seq(1,9)), seq(10, 12)), 2018 - 1991), "_", rep(seq(1991, 2018), each = 12))

# Correlation mean air temperature / water temperature
air_mean_temp <-
  rowMeans(tmean[, which(colnames(tmean) == "01_1995"):which(colnames(tmean) == "12_2018")]) 
air_temp <- enframe(air_mean_temp, name = "station", value = "air_95_18") %>%
  mutate(
    station = as.integer(station),
    air_06_18 = rowMeans(
      tmean[, which(colnames(tmean) == "01_2006"):which(colnames(tmean) == "12_2018")]
    )
  )

myload(habitat_press, sem_data, dir = mypath("data"))
temp_avg_comp <- habitat_press %>%
  dplyr::select(station, temperature_med) %>%
  left_join(air_temp, by = "station") %>%
  rename(water_06_2018 = temperature_med) %>%
  filter(station %in% sem_data$station)

dev.new(width = 6, height = 6, units = "cm")
# i3: mod + shift + space 
png(
  file = mypath("manuscript", "bef_stability", "figs",
    "pairs_temperature_plot.png")
)
pairs(
  temp_avg_comp[, 2:4], pch = 19 
)
dev.off()

mat <- round(cor(temp_avg_comp[, 2:4]), 3)
write.table(mat,
  file = mypath("manuscript", "bef_stability", "result", "cor_mat_temp.txt"),
  sep = ",",
  quote = FALSE,
  row.names = T)

# Test with monthly data
myload(yearly_temp_press_interp_mv_avg, dir = mypath("data-raw", "temp"))
temp <- yearly_temp_press_interp_mv_avg %>%
  group_by(id, year) %>%
  arrange(value.predSE) %>%
  slice(1) %>%
  select(station = id, year, temp = value_corrected) %>%
  mutate(temp = ifelse(temp > 45, NA, temp)) %>%
  ungroup()

#plot(pre[[1]])
#
#uk.area <- extent(-12, 4, 48, 64)
#uk <- crop(pre, uk.area)
#plot(uk)
#st <- get_basin_station(sf =TRUE)
#st_wgs <- st_transform(st, crs = 4326)
#
#test <- extract(pre, st_wgs)
```

@@

```{r}
myload(community_metrics, community_analysis,
  sem_data , dir = mypath("data"))
ti <- get_sync_cv_mat(com_analysis = community_analysis,
    op_analysis = op_analysis, presence_threshold = NA)

test <- ti %>%
  mutate(
    richness_tot = map_dbl(com_mat, ~ncol(.x)),
  ) %>%
select(station, richness_tot)
surf <- op_analysis %>%
  filter(station %in% sem_data$station) %>%
  group_by(station) %>%
  summarise(tot_surface = sum(surface), avg_surface = mean(surface))

surf_rich_tot <- surf %>%
  left_join(test, by = "station")

p_linear <- surf_rich_tot %>%
  ggplot(aes(x = tot_surface, y = (richness_tot))) +
  geom_point() +
  labs(y = "Total species richness", x = "Total surface (m^2)") +
  geom_smooth(method = "lm")
```

```{r}
test <- glm(richness_tot ~ tot_surface + I(tot_surface^2), family=quasipoisson, surf_rich_tot)
broom::tidy(test) %>%
  knitr::kable(, format = "rst")

```{r}
save_plot(file = mypath(
      "manuscript", "bef_stability", "result", 
      "richness_surface.png"),
    plot = p_linear,
    base_height = 9, base_asp = 1.2#1.618 
)
```

@@

p_sens_bm_rich <- plot_sensivity_analysis(
  .data = sem_bm_results_rich,
  inverse_label_order = TRUE, scale_color = FALSE,
  y_lim = c(-1.5, .75)
  ) +
geom_point(aes(colour = "pink", size = 4)) +
scale_color_manual(
  values =  cols_rich,
  labels = label_rich,
  breaks = names(label_rich)) +
  guides(color = guide_legend(direction = "horizontal", nrow = 1)) +
  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
```

@@

```{r rich-sens, fig.dim = c(10, 14), fig.cap="Sensivity of the standardized estimates to species richeness specification for the two structural equation model."}
legend_b <- get_legend(p_sens_stab_rich)
p <- plot_grid(
  p_sens_bm_rich %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm")),
  p_sens_stab_rich %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm")),
  legend_b, nrow = 3,
  rel_heights = c(1, 1, .1),
  labels = c("Total biomass", "Biomass stability")
)
p
```

### 2021-04-26 manuscript/bef_stability/table/hypothesis_sem.tex
Updates

\begin{tabular}{| m{7cm}| m{2cm}| m{4cm}|}
    \hline
    Link & hypothesis & reference\\
    \hline
    PCA1 Avg stream size $\to$ Species richness & (+) &
    \citet{post_ecosystem_2000, doi_resource_2009, mchugh_dual_2010} \\
    \hline
    PCA2 Avg temperature $\to$ Species richness & (+/-) & \citet{ogorman_unexpected_2017,gauzens_biodiversity_2020} \\
    \hline
    PCA1 Avg stream size $\to$ Connectance & ? & NA\\
    \hline
    PCA2 Avg temperature $\to$ Connectance & ? & NA\\
    \hline
    Species richness $\to$ Connectance & (-) & \citet{dunne_network_2006} \\
    \hline
    PCA1 Avg stream size $\to$ Avg trophic level & (+) & \citet{mchugh_dual_2010}\\
    \hline
    PCA2 Avg temperature $\to$ Avg trophic level & (+/-) & \citet{ogorman_unexpected_2017}\\
    \hline
    Species richness $\to$ Avg trophic level & ? & NA\\
    \hline
    Species richness $\to$ Synchrony & (-) & \citet{thebault_trophic_2005, loreau_species_2008, thibaut_understanding_2013} \\
    \hline
    Connectance $\to$ Synchrony & (+) & \citet{teng_dynamics_2004}\\
    \hline
    Avg trophic level $\to$ Synchrony & (+) & \citet{raimondo_interspecific_2004}\\
    \hline
    PCA1 Avg stream size $\to$ Synchrony & (-) & NA\\
    \hline
    PCA2 Avg temperature $\to$ Synchrony & (+) & \citet{loreau_species_2008}\\
    \hline
    Species richness $\to$ CVsp & (+) & \citep{tilman_biodiversity_1996} \\
    \hline
    Connectance $\to$ CVsp & NA & NA\\
    \hline
    Avg trophic level $\to$ CVsp & (-) & \citet{shanafelt_stability_2018}\\
    \hline
    PCA1 Avg stream size $\to$ CVsp & (-) & NA\\
    \hline
    PCA2 Avg temperature $\to$ CVsp & (+) & \citep{ogorman_unexpected_2017;tabi_warming_2019}\\
    \hline
    CVsp $\to$ Biomass stability & (-) & \citet{thibaut_understanding_2013}\\
    \hline
    Synchrony $\to$ Biomass stability & (-) & \citet{thibaut_understanding_2013}\\
    \hline
    Species richness $\to$ Total biomass & (+) & \citet{schneider_animal_2016}\\
    \hline
    Connectance $\to$ Total biomass & NA & \citet{wang_biodiversity_2018}\\
    \hline
    Avg trophic level $\to$ Total biomass & (+) & \citet{wang_biodiversity_2018}\\
    \hline
    PCA1 Avg stream size $\to$ Total biomass & (+) & \citet{post_ecosystem_2000, doi_resource_2009, @allan_stream_2007}\\
    \hline
    PCA2 Avg temperature $\to$ Total biomass & (+/-) & \citep{ogorman_unexpected_2017}\\
    \hline
\end{tabular}

>>>>

\begin{tabular}{| m{7cm}| m{2cm}| m{4cm}|}
    \hline
    Link & hypothesis & reference\\
    \hline
    PCA1 Avg stream size $\to$ Species richness & (+) & \citet{post_ecosystem_2000,doi_resource_2009,mchugh_dual_2010} \\
    \hline
    PCA2 Avg temperature $\to$ Species richness & (+/-) & \citet{ogorman_unexpected_2017,gauzens_biodiversity_2020} \\
    \hline
    PCA1 Avg stream size $\to$ Connectance & (?) & \\
    \hline
    PCA2 Avg temperature $\to$ Connectance & (+/-) & \citet{petchey_predicting_2010} \\
    \hline
    Species richness $\to$ Connectance & (-) & \citet{winemiller_must_1989, dunne_network_2006} \\
    \hline
    PCA1 Avg stream size $\to$ Avg trophic level & (+) &
    \citet{mchugh_dual_2010, doi_resource_2009, post_ecosystem_2000}\\
    \hline
    PCA2 Avg temperature $\to$ Avg trophic level & (+/-) & \citet{ogorman_unexpected_2017}\\
    \hline
    Species richness $\to$ Avg trophic level & (+) & \citet{schneider_animal_2016}\\
    \hline
    Species richness $\to$ Synchrony & (-) & \citet{thebault_trophic_2005, loreau_species_2008, thibaut_understanding_2013} \\
    \hline
    Connectance $\to$ Synchrony & (+) & \citet{teng_dynamics_2004}\\
    \hline
    Avg trophic level $\to$ Synchrony & (+) & \citet{raimondo_interspecific_2004}\\
    \hline
    PCA1 Avg stream size $\to$ Synchrony & (?) & \\
    \hline
    PCA2 Avg temperature $\to$ Synchrony & (+) & \citet{loreau_species_2008}\\
    \hline
    Species richness $\to$ CVsp & (+) & \citep{tilman_biodiversity_1996} \\
    \hline
    Connectance $\to$ CVsp & (+) & \citep{thebault_trophic_2005}\\
    \hline
    Avg trophic level $\to$ CVsp & (-) & \citet{mccann_more_2009, shanafelt_stability_2018}\\
    \hline
    PCA1 Avg stream size $\to$ CVsp & (?) & \\
    \hline
    PCA2 Avg temperature $\to$ CVsp & (+) & \citep{ogorman_unexpected_2017, tabi_warming_2019}\\
    \hline
    CVsp $\to$ Biomass stability & (-) & \citet{thibaut_understanding_2013}\\
    \hline
    Synchrony $\to$ Biomass stability & (-) & \citet{thibaut_understanding_2013}\\
    \hline
    Species richness $\to$ Total biomass & (+) & \citet{schneider_animal_2016}\\
    \hline
    Connectance $\to$ Total biomass & NA & \citet{wang_biodiversity_2018}\\
    \hline
    Avg trophic level $\to$ Total biomass & (+) & \citet{wang_biodiversity_2018}\\
    \hline
    PCA1 Avg stream size $\to$ Total biomass & (+) & \citet{post_ecosystem_2000, doi_resource_2009, @allan_stream_2007}\\
    \hline
    PCA2 Avg temperature $\to$ Total biomass & (+/-) & \citep{ogorman_unexpected_2017}\\
    \hline
\end{tabular}
